---
title: "Online Appendix"
author: "Anne"
date: "12/23/2021"
output: html_document

---

<style type="text/css">
  body{
  font-size: 14pt;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(rgl.useNULL = TRUE) # Suppress the separate window.
library(rgl)
```

# Multilevel polynomial regression analysis 

Multilevel polynomial regression analysis [MPRA; see @Nestler2019] is an adaptation of polynomial regression analysis [PRA; see @Edwards.1993a] that can be used when data have a multilevel structure (e.g., observations across multiple time points nested within participants). In the current study, MPRA allows testing and interpreting both the linear effects of vitality and learning separately, as well as the effects of congruent vitality and learning scores using data collected at four time points with a one-month time lag between the assessments. In the following, we use the index m to denote the Level 2 unit ($m = 1…N$) and the index $i$ to denote the Level 1 unit ($i = 1, 2, …, n_{m}$). To assess the existence of congruence effects, the following parameters are estimated at the population level: the slope of the line of congruence (LOC) (i.e., vitality = learning) as related to the outcome variable is given by $\alpha_{1m} = b_{1} + b_{2}$.  Here, $b_{1}$ is the unstandardized regression coefficient for the (latent) vitality variable and $b_2$ is the regression coefﬁcient for the (latent) learning variable. The curvature along the line of perfect agreement is specified by $\alpha_{1m} = b_{3} + b_{4} + b_{5}$. Here, $b_{3}$ is the regression coefﬁcient for (latent) vitality squared, b4 is the regression coefﬁcient for the cross-product of the (latent) vitality and the (latent) learning variable, and b5 is the unstandardized regression coefﬁcient for latent learning squared. The slope of the line of incongruence (LOIC) is defined as $\alpha_{3m} = b_{1} - b_{2}$. The curvature of the line of incongruent vitality and learning levels as related to the outcome variable is specified as $\alpha_{4m} = b_{3} - b_{4} + b_{5}$. Each of the regression coefficients $b_{1}$ to $b_{5}$ includes a fixed effect and Level 2 residual terms. The fixed effects of the regression coefficients are used to estimate the average response surface parameters $\hat{\alpha}_{1}$ to $\hat{\alpha}_{5}$ [@Nestler2019]. \

$~$

**References** \


<div id="refs"></div>

$~$

$~$

# Time-lagged correlations

```{r echo = FALSE}
corstar_select <- read_excel("../output/corstar_select.xlsx")
corstar_select$Mean <- sprintf("%.2f", corstar_select$Mean)
corstar_select$SD <- sprintf("%.2f", corstar_select$SD)

colnames(corstar_select) <- mgsub(colnames(corstar_select), 
                                  c("age", "sex", "edu", "tenure org", "aut", "csup", "ssup", "na", "pa", "sf12mcs", 
                                    "sf12pcs", "demands", "learn", "vitality", "thriv"),
                                  c("Age", "Gender", "Education", "Org. tenure", "Autonomy", "Cowork. support",
                                    "Superv. support","Negative affect", "Positive affect", "Mental health", 
                                    "Physical health", "Demands", "Learning", "Vitality", "Thriving"))
corstar_select <- corstar_select %>% remove_rownames %>% column_to_rownames(var="...1")
rownames(corstar_select) <- mgsub(rownames(corstar_select), 
                                  c("age", "sex", "edu", "tenure org", "aut", "csup", "ssup", "na", "pa", "sf12mcs", 
                                    "sf12pcs", "demands", "learn", "vitality", "thriv"),
                                  c("Age", "Gender", "Education", "Org. tenure", "Autonomy", "Cowork. support",
                                    "Superv. support","Negative affect", "Positive affect", "Mental health", 
                                    "Physical health", "Demands", "Learning", "Vitality", "Thriving"))
                                  

corstar_select %>%
  DT::datatable(
    caption = 'Note. N = 681-1,064 (pairwise deletion). T = time. *p < .05, **p < .01, ***p < .001',
    extensions = 'Buttons', 
    options = list(dom = 'Bfrtip', 
                   buttons = c('excel', "csv"),
                   pageLength = 10,
                  lengthMenu = c(10, 20, 30, 40,50)))

write.csv(corstar_select,"../../corstar_select.csv", row.names = TRUE) 

```

$~$

$~$


# Interactive response surface plots

## Physical health

The dots represent the raw data points. The x and y axes represent the person-mean centred vitality and learning scores, respectively. 


```{r echo = FALSE}
longer_comp <- read_csv("../../data/longer_comp.csv")


mphys_randomX_Y <- lmer(sf12pcs ~1 +CWC_x+CWC_y+CWC_x2+CWC_xy+CWC_y2+
                        GMC_T1_age+ GMC_T1_sex + GMC_T1_edu+ GMC_T1_tenure_org + 
                        CWC_pa + CWC_na + CWC_demands + CWC_aut + CWC_csup + CWC_ssup +
                        vitality.mean+learn.mean+vitality2.mean+vitalitylearn.mean+learn2.mean+ 
                        pa.mean+ na.mean + demands.mean + aut.mean + csup.mean + ssup.mean + set +
                        (1+CWC_x|ID),data=longer_comp,REML=F, control=lmerControl(optimizer="bobyqa"))


# PLOT THE ESTIMATED MODEL
# pdf(file = "Physheal.pdf")

name_vars=c("CWC_x","CWC_y","CWC_x2","CWC_xy","CWC_y2")

b0 <- fixef(mphys_randomX_Y)["(Intercept)"]
b1 <- fixef(mphys_randomX_Y)[name_vars[1]]
b2 <- fixef(mphys_randomX_Y)[name_vars[2]]
b3 <- fixef(mphys_randomX_Y)[name_vars[3]]
b4 <- fixef(mphys_randomX_Y)[name_vars[4]]
b5 <- fixef(mphys_randomX_Y)[name_vars[5]]

plotting_df <- longer_comp %>% select(CWC_x, CWC_y, sf12pcs)

write.csv(plotting_df,"../../response_surface.csv", row.names = TRUE) 
```



```{r echo= FALSE}
library(plotly)
library(geomorph)

set.seed(123)

x <- plotting_df$CWC_x

y <- plotting_df$CWC_y

z <- plotting_df$sf12pcs

  
z_pred = (b0 + (b1*x) + (b2*y) + (b3*(x**2)) + (b4*(x*y)) + (b5*(y**2)))

df <- data.frame(x, y, z, z_pred)

plot_ly(z = df, type = "surface") %>% 
  add_trace(text = "Data points", name = "Data point", data = df, x = x, y = y, z = z, mode = "markers", type = "scatter3d", 
            marker = list(size = 3.5, color = "#404788", symbol = 104)) %>%
  add_trace(text = "Prediction", name = "Prediction", data = df,  x = x, y = y, z = z_pred, type="mesh3d", color = "#efe350") %>%
  layout(showlegend = FALSE, 
         scene = list(
           xaxis = list(title = "Vitality"),
           yaxis = list(title = "Learning"),
           zaxis = list(title = "Physical health"),
           aspectratio = list(x=1, y=1, z=1)))

```





## Mental health

The dots represent the raw data points. The x and y axes represent the person-mean centred vitality and learning scores, respectively. 


```{r echo = FALSE}

mment_randomX_Y <- lmer(sf12mcs ~1 +CWC_x+CWC_y+CWC_x2+CWC_xy+CWC_y2+
                        GMC_T1_age+ GMC_T1_sex + GMC_T1_edu+ GMC_T1_tenure_org + 
                        CWC_pa + CWC_na + CWC_demands + CWC_aut + CWC_csup + CWC_ssup +
                        vitality.mean+learn.mean+vitality2.mean+vitalitylearn.mean+learn2.mean+ 
                        pa.mean+ na.mean + demands.mean + aut.mean + csup.mean + ssup.mean + set +
                        (1+CWC_x|ID),data=longer_comp,REML=F, control=lmerControl(optimizer="bobyqa"))


b0 <- fixef(mment_randomX_Y)["(Intercept)"]
b1 <- fixef(mment_randomX_Y)[name_vars[1]]
b2 <- fixef(mment_randomX_Y)[name_vars[2]]
b3 <- fixef(mment_randomX_Y)[name_vars[3]]
b4 <- fixef(mment_randomX_Y)[name_vars[4]]
b5 <- fixef(mment_randomX_Y)[name_vars[5]]

plotting_df <- longer_comp %>% select(CWC_x, CWC_y, sf12mcs)
```

```{r}
set.seed(123)

x <- plotting_df$CWC_x

y <- plotting_df$CWC_y

z <- plotting_df$sf12mcs

  
z_pred = (b0 + (b1*x) + (b2*y) + (b3*(x**2)) + (b4*(x*y)) + (b5*(y**2)))

df <- data.frame(x, y, z, z_pred)

plot_ly(z = df, type = "surface") %>% 
  add_trace(text = "Data point", name = "Data point", data = df, x = x, y = y, z = z, mode = "markers", type = "scatter3d", 
            marker = list(size = 3.5, color = "#404788", symbol = 104)) %>%
  add_trace(text = "Prediction", name = "Prediction", data = df,  x = x, y = y, z = z_pred, type="mesh3d", color = "efe350") %>%
  layout(showlegend = FALSE, 
         scene = list(
           xaxis = list(title = "Vitality"),
           yaxis = list(title = "Learning"),
           zaxis = list(title = "Mental health"),
           aspectratio = list(x=1, y=1, z=1)))

```


$~$

$~$



# Multilevel lagged analyses

$~$

## Measurement invariance

```{r}


#Model fit statistics for the test of measurement invariance for vitality and learning across T1 to T4

dataset <- read_csv("../../data/dataset.csv")

library(semTools)
model_configural <- '
Vita_T1     =~ T2_vitality1 + T2_vitality2 + T2_vitality5
Vita_T2     =~ T3_vitality1 + T3_vitality2 + T3_vitality5
Vita_T3     =~ T4_vitality1 + T4_vitality2 + T4_vitality5
Vita_T4     =~ T5_vitality1 + T5_vitality2 + T5_vitality5


Learn_T1    =~ T2_learn1 + T2_learn2 + T2_learn3 
Learn_T2    =~ T3_learn1 + T3_learn2 + T3_learn3 
Learn_T3    =~ T4_learn1 + T4_learn2 + T4_learn3 
Learn_T4    =~ T5_learn1 + T5_learn2 + T5_learn3 

'


longFacNames <- list(
  VITA =     c("Vita_T1","Vita_T2","Vita_T3", "Vita_T4"),
  LEARN =    c("Learn_T1","Learn_T2","Learn_T3", "Learn_T4"))


syntax.config <- measEq.syntax(configural.model = model_configural,
                               data = dataset,
                               ID.fac = "std.lv",
                               longFacNames = longFacNames,
                               auto="all")

mod.config <- as.character(syntax.config)   # save as text

fit.config <- cfa(mod.config, 
                  data = dataset, 
                  parameterization = "theta", 
                  estimator="ML",
                  missing="ML")


syntax.metric <- measEq.syntax(configural.model = model_configural, 
                               data = dataset,
                               ID.fac = "std.lv", 
                               longFacNames = longFacNames,
                               group.equal = c("loadings"),
                               long.equal  = c("loadings"),
                               auto="all")

mod.metric <- as.character(syntax.metric)   # save as text

## fit model to data
fit.metric <- cfa(mod.metric, 
                  data = dataset,
                  parameterization = "theta", 
                  estimator="ML",
                  missing="ML")


syntax.strong <- measEq.syntax(configural.model = model_configural, 
                               data = dataset,
                               parameterization = "theta",
                               ID.fac = "std.lv", 
                               longFacNames = longFacNames,
                               group.equal = c("loadings", "intercepts"),
                               long.equal  = c("loadings", "intercepts"),
                               auto="all")

mod.strong<- as.character(syntax.strong)    # save as text

## fit model to data
fit.strong<- cfa(mod.strong, 
                  data = dataset,
                  parameterization = "theta", 
                  estimator="ML",
                  missing="ML")


syntax.strict <- measEq.syntax(configural.model = model_configural, 
                               data = dataset,
                               ID.fac = "std.lv", 
                               longFacNames = longFacNames,
                               group.equal = c("loadings", "intercepts", "means"),
                               long.equal  = c("loadings", "intercepts", "means"),
                               auto="all")

mod.strict<- as.character(syntax.strict)   # save as text

## fit model to data
fit.strict<- cfa(mod.strict, 
                  data = dataset, 
                  parameterization = "theta", 
                  estimator="ML",
                  missing="ML")


fit_compare <- compareFit(fit.config, fit.metric, fit.strong, fit.strict, nested = TRUE)@fit

fit_compare <- fit_compare %>% select(matches("^chisq$|^df$|^pvalue$|cfi|tli|rmsea$|srmr$"))

require(data.table)
df <- data.table(fit_compare)
#setDT(df) #if df is already a data frame

df[ , diff_chisq := chisq - shift(chisq)] 
df[ , diff_df := df - shift(df)] 
df[ , diff_cfi := cfi - shift(cfi)] 
df[ , diff_tli := tli - shift(tli)] 
df[ , diff_rmsea := rmsea - shift(rmsea)] 
df[ , diff_srmr := srmr - shift(srmr)] 

fit_table <- as.data.frame(df) %>% 
  mutate_if(is.numeric, funs(sprintf("%.3f", round(., 3))))

fit_table$chisq <- (paste(fit_table$chisq, " (", gsub(".000", "", fit_table$df),  ")", sep=""))
fit_table$pvalue <- gsub("0.", ".", fit_table$pvalue, fixed = TRUE)
fit_table$pvalue <- gsub(".000", "<.001", fit_table$pvalue, fixed = TRUE)
fit_table$diff_chisq <- (paste(fit_table$diff_chisq, " (", gsub(".000", "", fit_table$diff_df),  ")", sep=""))
fit_table <- map_df(fit_table, ~ gsub("-0.000", "<0.001", .x))
fit_table <- map_df(fit_table, ~ gsub("0.000", "<0.001", .x))
fit_table <- map_df(fit_table, ~ gsub("- (-)", "-", .x))
fit_table <- map_df(fit_table, ~ gsub("NA (NA)", "-", fixed = TRUE, .x))
fit_table <- map_df(fit_table, ~ gsub("NA", "-", .x))
fit_table <- fit_table %>% select(chisq, pvalue, cfi, tli, rmsea, srmr, diff_chisq, diff_cfi, diff_tli, diff_rmsea, diff_srmr)
fit_table <- cbind(`Model test` = 0, fit_table)
fit_table$`Model test`<- c("Configural invariance", "Weak invariance", "Strong invariance", "Strict invariance")

colnames(fit_table) <- c("Model test", "$\\chi^2$","$\\textit{p}$", "CFI", "TLI", "RMSEA", "SRMR", "$\\Delta\\chi^2$","$\\Delta$CFI", "$\\Delta$TLI", "$\\Delta$RMSEA", "$\\Delta$SRMR")


knitr::kable(fit_table, caption = "N = 1,064. CFI = comparative fit index; TLI = Tucker–Lewis index; RMSEA = root mean square error of approximation; SRMR = standardized root mean square residual.") %>%  kable_styling(font_size = 12)


```

$~$

## Physical health

Lagged multilevel model including the effects of predictors measured at t-1 on physical health measured at t


```{r echo = FALSE}
longer_comp_l <- read_csv("../../data/longer_comp_l.csv")

mphys_randomX_Y_lagged<- lmer(Physical.health ~1 +Vitality+Learning+ Vitality.squared+ Vitality.x.learning +Learning.squared+
                        Positive.affect+ Negative.affect + Demands+ Autonomy + 
                        Coworker.support + Supervisor.support + Time + 
                          Mean.vitality + Mean.learning + Mean.vitality.squared + Mean.vitality.x.learning + Mean.learning.squared +
                        Mean.positive.affect + Mean.negative.affect+ Mean.demands+ 
                          Mean.autonomy+ Mean.coworker.support+ Mean.supervisor.support +  
                          Age + Gender + Education + Organizational.tenure + `T-1.Physical.health` +
                        (1+Vitality|Person.ID),data=longer_comp_l,REML=F, control=lmerControl(optimizer="bobyqa"))


mphys_random_thriv_lagged<- lmer(Physical.health ~1 +Thriving+
                        Positive.affect+ Negative.affect + Demands+ Autonomy + 
                        Coworker.support + Supervisor.support + Time + 
                          Mean.thriving + 
                        Mean.positive.affect + Mean.negative.affect+ Mean.demands+ 
                          Mean.autonomy+ Mean.coworker.support+ Mean.supervisor.support +  
                          Age + Gender + Education + Organizational.tenure + `T-1.Physical.health` +
                        (1+Thriving|Person.ID),data=longer_comp_l,REML=F, control=lmerControl(optimizer="bobyqa"))


tab2 <- tab_model(c(mphys_random_thriv_lagged, mphys_randomX_Y_lagged), show.ci = FALSE, show.se = TRUE, digits.re = 3, show.std = TRUE, 
                  title = "Model 1:Physical health predicted by thriving and control variables; Model 2: Physical health predicted by learning and vitality linear, interaction, and squared terms and control variables.", string.est = "b",string.se = "SE",  string.std = "beta",
                   order.terms = c(1, 21, 2, 22:26, 3:9, 27:31, 10:20), 
                   string.std_se = "SE beta", dv.labels = c("Model 1", "Model 2"))


tab2

```

$~$

## Mental health

Lagged multilevel model including the effects of predictors measured at t-1 on mental health measured at t


```{r echo = FALSE}
longer_comp_l <- read_csv("../../data/longer_comp_l.csv")

mment_randomX_Y_lagged<- lmer(Mental.health ~1 +Vitality+Learning+ Vitality.squared+ Vitality.x.learning +Learning.squared+
                        Positive.affect+ Negative.affect + Demands+ Autonomy + 
                        Coworker.support + Supervisor.support + Time + 
                          Mean.vitality + Mean.learning + Mean.vitality.squared + Mean.vitality.x.learning + Mean.learning.squared +
                        Mean.positive.affect + Mean.negative.affect+ Mean.demands+ 
                          Mean.autonomy+ Mean.coworker.support+ Mean.supervisor.support +  
                          Age + Gender + Education + Organizational.tenure + `T-1.Mental.health` +
                        (1+Vitality|Person.ID),data=longer_comp_l,REML=F, control=lmerControl(optimizer="bobyqa"))


mment_random_thriv_lagged<- lmer(Mental.health ~1 +Thriving+
                        Positive.affect+ Negative.affect + Demands+ Autonomy + 
                        Coworker.support + Supervisor.support + Time + 
                          Mean.thriving + 
                        Mean.positive.affect + Mean.negative.affect+ Mean.demands+ 
                          Mean.autonomy+ Mean.coworker.support+ Mean.supervisor.support +  
                          Age + Gender + Education + Organizational.tenure + `T-1.Mental.health` +
                        (1+Thriving|Person.ID),data=longer_comp_l,REML=F, control=lmerControl(optimizer="bobyqa"))


tab2 <- tab_model(c(mment_random_thriv_lagged, mment_randomX_Y_lagged), show.ci = FALSE, show.se = TRUE, digits.re = 3, show.std = TRUE, 
                  title = "Model 1:Mental health predicted by thriving and control variables; Model 2: Mental health predicted by learning and vitality linear, interaction, and squared terms and control variables.", string.est = "b",string.se = "SE",  string.std = "beta",
                   order.terms = c(1, 21, 2, 22:26, 3:9, 27:31, 10:20), 
                   string.std_se = "SE beta", dv.labels = c("Model 1", "Model 2"))


tab2

```





